Synthesis of Linear Functional Programs

### 2021-07-15 article/article.tex
tweaks

Despite their long-known potential (\emph{linear types can change the
world!}\cite{Wadler90lineartypes}, \cite{DBLP:journals/mscs/CairesPT16,Bernardy_2018}) and,
primarily, strong proof-theoretic
foundations \cite{10.1093/logcom/2.3.297,DBLP:conf/cade/ChaudhuriP05,DBLP:journals/tcs/CervesatoHP00}, synthesis of linear functional programs
from linear types hasn't been previously explored in an extended context (e.g.
with recursion, polymorphism, ...).
%TODO: Sinto que faltam algumas palavras aqui..

@@

However, a programming language only with the canonical linear types lacks
expressiveness. To enhance \synname\ and its language, synthetise more interesting
programs -- and thus empirically proving the feasability of more relevant
synthesis in a linear context, we extend the syntax and type system with
recursiveness and richer
types: -- polimorfic, refinements, adts parametrizáveis...  todo

>>>>

Despite their long-known potential (\emph{linear types can change the
world!}\cite{Wadler90lineartypes}, \cite{DBLP:journals/mscs/CairesPT16,Bernardy_2018}) and,
primarily, strong proof-theoretic
foundations \cite{10.1093/logcom/2.3.297,DBLP:conf/cade/ChaudhuriP05,DBLP:journals/tcs/CervesatoHP00}, synthesis of linear functional programs
from linear types hasn't been previously explored in an ``advanced'' context (e.g.
with recursion, polymorphism, ...).
%TODO: Sinto que faltam algumas palavras aqui..

@@

However, a programming language only with the canonical linear types lacks
expressiveness. To enhance \synname\ and its language, synthetise more interesting
programs -- and thus empirically prove the feasability of more relevant
synthesis in a linear context, we extend the syntax and type system with
recursiveness and richer
types: -- polimorfic, refinements, adts parametrizáveis...  todo
